openTSNE: a modular \proglang{Python} library for t-SNE dimensionality reduction and embedding

### 2023-05-22 2023-05-revision-1/main.tex
Mention Laplacian eigenmaps in initialization section

\citet{kobak2019umap} showed that the initialization of force-directed layout
algorithms, such as t-SNE, UMAP~\citep{2018arXivUMAP}, and
ForceAtlas2~\citep{jacomy2014forceatlas2}, largely dictates the global
consistency of resulting embeddings. When initialized randomly, clusters are
often arbitrarily scattered in the embedding space. However, when using
initialization schemes based on PCA or spectral embeddings, the clusters
identified in the resulting embedding are typically grouped in a globally
coherent manner.

@@

\item The optimization in t-SNE starts with initial positions for each data point in the embedding space. We can set the initial positions randomly or impose an initial global structure on the embedding with, for example, a PCA-based initialization. Accordingly, the \code{openTSNE.initialization} module provides several possible initialization schemes, The user can also specify their initialization by providing a \code{numpy.ndarray} object. By default, \opentsne opts for PCA-based initialization.

>>>>

\citet{kobak2019umap} showed that the initialization of force-directed layout
algorithms, such as t-SNE, UMAP~\citep{2018arXivUMAP}, and
ForceAtlas2~\citep{jacomy2014forceatlas2}, largely dictates the global
consistency of resulting embeddings. When initialized randomly, clusters are
often arbitrarily scattered in the embedding space. However, when using
initialization schemes based on PCA or Laplacian eigenmaps~\citep{belkin2001laplacian}, the clusters identified in the resulting embedding are typically grouped in a globally
coherent manner.

@@

\item The optimization in t-SNE starts with initial positions for each data point in the embedding space. We can set the initial positions randomly or impose an initial global structure on the embedding. % with, for example, a PCA-based initialization.
The \code{openTSNE.initialization} module provides several possible initialization schemes including random, PCA-based, and Laplacian Eigenmap-based intialization schemes. The user can also specify their own initialization by providing a \code{numpy.ndarray} object. By default, \opentsne opts for PCA-based initialization.
